Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-07-21 docs/paper/paper.Rmd
add more description of forecats patterns

# Partial coverage models
partial_models <- locations_per_model |>
  DT(n > 1) |>
  DT(n <= 30)

# Models coverage of forecast datees
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "target_end_date", by = "model") |>
  DT(order(n))
```

@@

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as "epiforecasts-EpiNow2" by the hub), and our surrogate model (referred to as "epiforecasts-weeklygrowth" by the hub). Of the remainining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r length(partial_models)` models submitted for between 2 and 30 locations likely indicating manual curation of submissions.

Across all forecast dates and locations the minimum number of independent forecasts was `r models_per_loc_date[, min(n)]` with the maxmimum being `r models_per_loc_date[, max(n)]`. The median number of independent forecasts per location and forecast date was `r models_per_loc_date[, median(n)]`. Across all forecast dates all locations recieved forecasts from at least `r models_per_location[, min(n)]` models with the median number of forecast models per location being `r models_per_location[, median(n)]`.

- Date range of forecasts
- Forecasts per country
- Total number of forecast models and average per location and per forecast date
- Summarises general trends in incidence in the data

>>>>

# Partial coverage models
partial_models <- locations_per_model |>
  DT(n > 2) |>
  DT(n <= 30)

#Varying submissions
varying_submissions <- locs_per_model_date |>
  DT(partial_models[, .(model)], on = "model")

# Models coverage of forecast datees
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "target_end_date", by = "model") |>
  DT(order(n)) |>
  DT(, n_per := n / forecast_dates) |>
  DT(, type := fcase(
      model %in% global_models, "global",
      model %in% local_models, "local",
      model %in% partial_models[, model], "partial",
      default = "other"
    )
  )
```

@@

- Incidence in the ECDC
  - Omicron variant
  - BA.1 and BA.2 variant
  - Differences across countries and timings
  - NPIs across countries
  - testing across countries

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as "epiforecasts-EpiNow2" by the hub), and our surrogate model (referred to as "epiforecasts-weeklygrowth" by the hub). Of the remaining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r length(partial_models)` models submitted for between 3 and 30 locations and all these models varied the number of locations they submitted forecasts for over time, potentially indicating manual curation or models targted at specific conditions.

Across all forecast dates and locations the minimum number of independent forecasts was `r models_per_loc_date[, min(n)]` with the maxmimum being `r models_per_loc_date[, max(n)]`. The median number of independent forecasts per location and forecast date was `r models_per_loc_date[, median(n)]`. All locations recieved forecasts from at least `r models_per_location[, min(n)]` models with the median number of forecast models per location being `r models_per_location[, median(n)]`. Coverage of forecast dates varied across submitted models with `r forecast_dates_by_models[n_per == 1, .N]` models submitting for all dates, `r forecast_dates_by_models[n_per >= 0.9, .N]` models submitting for at least 90% of dates, and `r forecast_dates_by_models[n_per < 0.50, .N]` models submitting for fewer than 50% of forecast dates. In general, there was no clear difference in forecast date coverage between models that submitted for all locations vs a small subset but models with partial coverage of locations all also had partial coverage of forecast dates.
